Something something values disclosure replication

### 2022-07-12 paper/paper.Qmd
both html and pdf formats available

---
title: "Something something values disclosure replication"
author: "Daniel J. Hicks and Emilio Lobato"
abstract: |
  abstract
toc: true
execute:
    echo: false
bibliography: |
  transparency-Hicks.yaml
header-includes:
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\landscape}
  - \newcommand{\elandscape}{\endlandscape}
  # - \usepackage{endfloat}
---

@@

+------------------+------------------------------------------+-------------+
|                  | Hypothesis                               | Replicated? |
+==================+==========================================+=============+
|              H1a | Liberals prioritize public health        | yes         |
|                  | rel. to conservatives                    |             |
+------------------+------------------------------------------+-------------+
|              H1b | Majority of conservatives prioritize     | no          |
|                  | public health                            |             |
+------------------+------------------------------------------+-------------+
|               H2 | Sci. who find chemical is harmful        | yes         |
|                  | perceived as more trustworthy            |             |
+------------------+------------------------------------------+-------------+
|               H3 | Sci. who disclose values perceived as    | no          |
|                  | less trustworthy                         |             |
+------------------+------------------------------------------+-------------+
|               H4 | Given sci. discloses values,             | no          |
|                  | sci. who shared values with participant  |             |
|                  | perceived as more trustworthy            |             |
+------------------+------------------------------------------+-------------+
|        Unplanned | Given sci. discloses values,             |yes$^\dagger$|
|                  | sci. who values public health            |             |
|                  | perceived as more trustworthy            |             |
+------------------+------------------------------------------+-------------+
|      H5-consumer | Interaction btwn. sci. conclusion (H2)   | yes         |
|                  | and participant values                   |             |
+------------------+------------------------------------------+-------------+
|  H5-transparency | Interaction btwn. values disclosure (H3) | no          |
|                  | and participant values                   |             |
+------------------+------------------------------------------+-------------+
|        H5-shared | Interaction btwn. shared values (H4)     | $^\star$    |
|                  | and participant values                   |             |
+------------------+------------------------------------------+-------------+
|   H5-sci. values | Interaction btwn. scientist values       | no$^\dagger$|
|                  | and participant values                   |             |
+------------------+------------------------------------------+-------------+

>>>>

---
title: "Something something values disclosure replication"
author: "Daniel J. Hicks and Emilio Lobato"
abstract: |
  abstract
toc: true
execute:
    echo: false
bibliography: |
  transparency-Hicks.yaml
format: 
    html: default
    pdf: default
---

@@

+-------------------+------------------------------------------+-------------+
|                   | Hypothesis                               | Replicated? |
+===================+==========================================+=============+
|               H1a | Liberals prioritize public health        | yes         |
|                   | rel. to conservatives                    |             |
+-------------------+------------------------------------------+-------------+
|               H1b | Majority of conservatives prioritize     | no          |
|                   | public health                            |             |
+-------------------+------------------------------------------+-------------+
|                H2 | Sci. who find chemical is harmful        | yes         |
|                   | perceived as more trustworthy            |             |
+-------------------+------------------------------------------+-------------+
|                H3 | Sci. who disclose values perceived as    | no          |
|                   | less trustworthy                         |             |
+-------------------+------------------------------------------+-------------+
|                H4 | Given sci. discloses values,             | no          |
|                   | sci. who shared values with participant  |             |
|                   | perceived as more trustworthy            |             |
+-------------------+------------------------------------------+-------------+
|         Unplanned | Given sci. discloses values,             |yes$^\dagger$|
|                   | sci. who values public health            |             |
|                   | perceived as more trustworthy            |             |
+-------------------+------------------------------------------+-------------+
|       H5-consumer | Interaction btwn. sci. conclusion (H2)   | yes         |
|                   | and participant values                   |             |
+-------------------+------------------------------------------+-------------+
|   H5-transparency | Interaction btwn. values disclosure (H3) | no          |
|                   | and participant values                   |             |
+-------------------+------------------------------------------+-------------+
|         H5-shared | Interaction btwn. shared values (H4)     | $^\star$    |
|                   | and participant values                   |             |
+-------------------+------------------------------------------+-------------+
|    H5-sci. values | Interaction btwn. scientist values       | no$^\dagger$|
|                   | and participant values                   |             |
+-------------------+------------------------------------------+-------------+
